Can We Crunch the Social Graph on the Cheap?

### 2011-01-26 doc/hotpar2011/softxmt-hotpar2011.tex

%todo format the UW names horizontally
\authorinfo{Jacob Nelson, Brandon Myers, Andrew Hunter, Dan Grossman, Mark Oskin,
Carl Ebeling, Luis Ceze}{University of Washington}{\{nelson, bdmyers, ahh, djg, oskin, ebelin, luisceze\}@cs.washington.edu}
\authorinfo{Simon Kahan}{Pacific Northwest National Lab}{skahan@cs.washington.edu}
\authorinfo{Preston Briggs}{}{preston.briggs@gmail.com}

\maketitle
\begin{abstract}

Techniques from graph analytics have found important applications in
areas such as social networks and bioinformatics. These irregular
problems present a challenge for parallel machines: obtaining
performance is not straightforward. Multithreading works well for
such problems, but the only large-scale implementation of the technique
is the Cray XMT, an expensive, non-commodity machine.

Our goal is to build a system with XMT-like properties, implemented
with commodity components. This paper presents a runtime for latency
tolerance, along with our plans for scaling up to multiple
nodes. Our analysis shows the feasibility of our approach.
\end{abstract}

>>>>

%todo format the UW names horizontally
\authorinfo{Jacob Nelson, Brandon Myers, A.H. Hunter, Dan Grossman, Mark Oskin,
Carl Ebeling, Luis Ceze}{University of Washington}{\{nelson, bdmyers, ahh, djg, oskin, ebelin, luisceze\}@cs.washington.edu}
\authorinfo{Simon Kahan}{Pacific Northwest National Lab}{skahan@cs.washington.edu}
\authorinfo{Preston Briggs}{}{preston.briggs@gmail.com}

\maketitle
\begin{abstract}
% Techniques from graph analytics have found important applications in
% areas such as social networks and bioinformatics. These irregular
% problems present a challenge for parallel machines: obtaining
% performance is not straightforward. Multithreading works well for
% such problems, but the only large-scale implementation of the technique
% is the Cray XMT, an expensive, non-commodity machine.

% Our goal is to build a system with XMT-like properties, implemented
% with commodity components. This paper presents a runtime for latency
% tolerance, along with our plans for scaling up to multiple
% nodes. Our analysis shows the feasibility of our approach.

  Large, sparse, irregular graphs map poorly to the memory systems of
  commodity hardware. The scale of emerging real world datasets
  presents a challenge for straightforward algorithms which will run
  inefficiently due to many high-latency accesses.  Pervasive
  parallelism can tolerate that latency, but the only large-scale
  implementation of the technique is the Cray XMT, an expensive,
  non-commodity machine.

  If we can adapt the XMT's programming model to commodity hardware,
  we can dramatically improve performance without resorting to
  expensive custom systems. This paper presents a runtime for latency
  tolerance through the use of parallel lightweight contexts, along
  with our plans for scaling up to multiple nodes. Our analysis shows
  the feasibility of our approach.
\end{abstract}
